A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array

### 2014-10-24 foreground_delay_spectrum_modeling.tex
Explanation added for approximation between eta and k_parallel

Since we are concerned with a redshifted H{\sc i} spectral line from cosmological distances, $f$ is a measure of cosmological distance along the line of sight. $\eta$, which is the Fourier transform dual of $f$, is used to denote the spatial frequency along the line of sight and has units of time. It is directly related to the line--of--sight wavenumber, $k_\parallel\approx 2\pi\eta\,f_{21}H_0\,E(z)/(c(1+z)^2)$, where $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H{\sc i}, and $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. Thus,
\begin{align}\label{eqn:los-transform}
  V_{u\eta}(\vec{u},\eta) &= \int V_{uf}(\vec{u},f)\,W'_f(f)\,e^{i2\pi f\eta}\,\dif f
\end{align}
represents the true spatial Fourier representation of the three--dimensional sky brightness distribution. This representation has been discussed in detail in \citet{mor04}. The spatial power spectrum of EoR H{\sc i} distribution, $P(\vec{k}_\perp,k_\parallel)$, and $V_{u\eta}(\vec{u},\eta)$ are related by $P(\vec{k}_\perp,k_\parallel)\propto |V_{u\eta}(\vec{u},\eta)|^2$.

@@

Figure~\ref{fig:fourier-space} illustrates the Fourier space in which the delay (and power) spectra of H{\sc i} from the EoR are presented in this paper. $|\vec{b}|$ and $k_\perp$, denoting spatial scales in the transverse direction, form the $x$--axis. $\tau\approx\eta\propto k_\parallel$, denoting spatial scales along line--of--sight form the $y$--axis. Foreground emission maps to a wedge--shaped region in Fourier space, hereafter referred to as the {\it foreground wedge} \citep{dat10}, whose boundaries are determined by antenna spacing and the light travel time across it. These boundaries are called horizon delay limits and are shown by solid lines. The spectral transfer function of the instrument convolves the {\it foreground wedge} and stretches it further (unshaded narrow strips bounded by solid and dashed lines) along $\tau$--axis. This effect has been quantified in \citet{thy13}. The width of this narrow strip is inversely proportional to the operating bandwidth. The region of Fourier space excluding the {\it foreground wedge} and the narrow strips is the so--called {\it EoR window}, shown in light and medium shades. However, the instrument used in our study, namely the MWA, has a passband constructed using coarse channels with a characteristic shape giving rise to periodic gratings thereby resulting in repetitions of the {\it foreground wedge} at multiples of 0.78~$\mu$s.

>>>>

Since we are concerned with a redshifted H{\sc i} spectral line from cosmological distances, $f$ is a measure of cosmological distance along the line of sight. $\eta$, which is the Fourier transform dual of $f$, is used to denote the spatial frequency along the line of sight and has units of time. It is directly related to the line--of--sight wavenumber, $k_\parallel\approx 2\pi\eta\,f_{21}H_0\,E(z)/(c(1+z)^2)$, where $f_{21}$ is the rest frame frequency of the 21~cm spin flip transition of H{\sc i}, and $H_0$ and $E(z)\equiv [\Omega_\textrm{M}(1+z)^3+\Omega_\textrm{k}(1+z)^2+\Omega_\Lambda]^{1/2}$ are standard terms in cosmology. This approximation holds under the assumption that there is negligible cosmological evolution within the redshift range (or frequency band). Thus,
\begin{align}\label{eqn:los-transform}
  V_{u\eta}(\vec{u},\eta) &= \int V_{uf}(\vec{u},f)\,W'_f(f)\,e^{i2\pi f\eta}\,\dif f
\end{align}
represents the true spatial Fourier representation of the three--dimensional sky brightness distribution. This representation has been discussed in detail in \citet{mor04}. The spatial power spectrum of EoR H{\sc i} distribution, $P(\vec{k}_\perp,k_\parallel)$, and $V_{u\eta}(\vec{u},\eta)$ are related by $P(\vec{k}_\perp,k_\parallel)\propto |V_{u\eta}(\vec{u},\eta)|^2$.

@@

Figure~\ref{fig:fourier-space} illustrates the Fourier space in which the delay (and power) spectra of H{\sc i} from the EoR are presented in this paper. $|\vec{b}|$ and $k_\perp$, denoting spatial scales in the transverse direction, form the $x$--axis. $\tau\approx\eta\propto k_\parallel$, denoting spatial scales along line--of--sight form the $y$--axis. Foreground emission maps to a wedge--shaped region in Fourier space, hereafter referred to as the {\it foreground wedge} \citep{dat10}, whose boundaries are determined by the antenna spacings and the light travel times across them. These boundaries are called horizon delay limits and are shown by solid lines. The spectral transfer function of the instrument convolves the {\it foreground wedge} and stretches it further (unshaded narrow strips bounded by solid and dashed lines) along $\tau$--axis. This effect has been quantified in \citet{thy13}. The width of this narrow strip is inversely proportional to the operating bandwidth. The region of Fourier space excluding the {\it foreground wedge} and the narrow strips is the so--called {\it EoR window}, shown in light and medium shades. However, the instrument used in our study, namely the MWA, has a passband constructed using coarse channels with a characteristic shape giving rise to periodic gratings thereby resulting in repetitions of the {\it foreground wedge} at multiples of 0.78~$\mu$s.
